Software Ticket Quality

### 2017-11-15 proposal/mprop.tex
Add paper on stack traces in bug reports

\textbf{Software Process Data Quality and Characteristics}\cite{bachmann2009software}:
\begin{itemize}
  \item \textbf{What were the goals?}
    The authors are trying to investigate different software process data
    (e.g. bug tracking databases, version control systems logs) in order to
    infer quality and characteristics. Then, they want to compute measures
    and discuss the issues that arise from these observations.
  \item \textbf{What was the method?}
    They examined 6 software projects, 5 of which were open source, by extracting
    the SVN and CSV logs, as well as the content of the bug tracker databases. Then,
    they tried to link the logs with the contents of the bug tracker databases as they
    are not integrated by default. 
  \item \textbf{What did they learn?}
    Firstly, the closed source project the authors examined showed much more data
    quality as the open source counterparts, among which better average attachments 
    per bug report, better average status changes per bug report or average commits
    per bug report/developer. Moreover, the authors found that there is little linkage
    between bug reports and version control logs, thus reducing the overall traceability.
    Also, there is reduced quality in change logs as, for example, the Eclipse project
    has more than 20\% empty commit messages. In conclusion, closed source projects will
    probably exhibit improved data quality than open source ones, but data quality in general
    differs from project to project.
  \item \textbf{Relevance to our work}:
    The analysis on data quality in open/closed source projects presented in this 
    research is valuable to us as it presents various statistics on commits, bug report
    structure and quality, as well as linkage between the two. We might apply the techniques
    in our own research on ticket quality.
\end{itemize}

@@

>>>>

\textbf{Software Process Data Quality and Characteristics}\cite{bachmann2009software}:
\begin{itemize}
  \item \textbf{What were the goals?}
    The authors are trying to investigate different software process data
    (e.g. bug tracking databases, version control systems logs) in order to
    infer quality and characteristics. Then, they want to compute measures
    and discuss the issues that arise from these observations.
  \item \textbf{What was the method?}
    They examined 6 software projects, 5 of which were open source, by extracting
    the SVN and CVS logs, as well as the content of the bug tracker databases. Then,
    they tried to link the logs with the contents of the bug tracker databases as they
    are not integrated by default. 
  \item \textbf{What did they learn?}
    Firstly, the closed source project the authors examined showed much more data
    quality as the open source counterparts, among which better average attachments 
    per bug report, better average status changes per bug report or average commits
    per bug report/developer. Moreover, the authors found that there is little linkage
    between bug reports and version control logs, thus reducing the overall traceability.
    Also, there is reduced quality in change logs as, for example, the Eclipse project
    has more than 20\% empty commit messages. In conclusion, closed source projects will
    probably exhibit improved data quality than open source ones, but data quality in general
    differs from project to project.
  \item \textbf{Relevance to our work}:
    The analysis on data quality in open/closed source projects presented in this 
    research is valuable to us as it presents various statistics on commits, bug report
    structure and quality, as well as linkage between the two. We might apply the techniques
    in our own research on ticket quality.
\end{itemize}

@@

\textbf{Do Stack Traces Help Developers Fix Bugs?}\cite{schroter2010stack}:
\begin{itemize}
  \item \textbf{What were the goals?}
    The main goal of the paper was to identify if including a stack trace in a 
    bug report would help the developers fix the issue quicker. They divided their
    investigations in order to follow 4 research questions:
      \begin{itemize}
        \item are bugs fixed in methods in stack traces;
        \item how far down the stack to trace;
        \item are two or more stack traces better than one;
        \item do stack traces help speed up debugging.
  \item \textbf{What was the method?}
    They conducted their investigation on the Eclipse project which is developed in
    Java. Then, they extracted stack traces from bug reports using the infoZilla tool.
    Afterwards, they linked the stack traces (and thus the corresponding bug report)
    to changes in the source code (change logs) by mining the version repository of the
    Eclipse project.
  \item \textbf{What did they learn?}
    They found answers to all their research questions, and are as follows:
      \begin{itemize}
        \item around 60\% of the bugs that contained stack traces were fixed in 
        one of the methods in the frames;
        \item around 40\% were fixed in the first stack frame, around 80\% were fixed
        within the top 6 frames, while close to 90\% of the bugs were fixed within top 10 stack frames;
        \item having more than one stack trace usually helped more than only a single one;
        \item bug reports containing stack traces usually have a shorter lifetime, thus
        speeding up the debugging process.
      \end{itemize}
  \item \textbf{Relevance to our work}:
    Stack traces are one of the types of information we are investigating in our research
    and it is very useful to have such a study back up the statement that stack traces are
    valuable for developers so that they speed up the issue fixing process.
\end{itemize}
